Avoidance in permutations

### 2014-11-07 project2/paper/paper.tex
comments and changes in section 6

Studying avoidance of permutations in $T_n$ seems an interesting exercise. In this section, we consider the sequence of numbers $t_n(\pi)$, defined as 
\[t_n(\pi)=\#\{\sigma\in T_n|\sigma \text{ avoids } \pi\},\]
with $\pi\in S_3$.

@@

The above two claims shows there's actually an easy way to transform an arbitrary permutation $a \in A$ to a $b \in B$, and similarly, to transform an arbitrary permutation $b \in B$ to a $a \in A$ -- to obtain a permutation in $B$ from a permutation $a \in A$, for every element $i$ in the permutation $a$, all even elements in $a$ to the right of $i$ less than $i$ should be reversed (that is reordered to in increasing order); similarly to obtain a permutation in $A$ from a permutation $b \in B$, for every element $i$ in the permutation $b$, all even elements in $b$ to the right of $i$, less than $i$ should be reversed (that is reordered to in decreasing order). \todo{should have some justification here that reversing reordering these elements doesn't 'step on each other'... that is, you can always do it for some $i_1$ and then some $i_2$ afterward}
Since the mapping from $A$ to $B$ is clearly reversible, and hence invertible, we conclude that the mapping we just established between $A$ and $B$ is bijective.

@@

\begin{proof}
As before, proving the above theorem is equivalent to proving that the $m^{th}$ term of $t_n(213)$ is equal to $2^{m-1}$, or that the number of permutations in $T_{2m}$ that avoid $213$ is equal to $2^{m-1}$.

@@

Note that even though we proved that the sequences $t_n(231)$ and $t_n(213)$ are both equivalent, the methods used to prove that each sequence is equal to the sequence $1, 2, 4, 8, \ldots$ are vastly different -- this is an interesting topic of research that we would like to pursue as future work.

>>>>

We will now study avoidance of permutations in $T_n$. In this section, we consider the sequence of numbers $t_n(\pi)$, defined as 
\[t_n(\pi)=\#\{\sigma\in T_n|\sigma \text{ avoids } \pi\},\]
with $\pi\in S_3$.

@@

\todo{this is a really long sentence}The above two claims show that there is actually an easy way to transform an arbitrary permutation $a \in A$ to a $b \in B$, and similarly, to transform an arbitrary permutation $b \in B$ to a $a \in A$ -- to obtain a permutation in $B$ from a permutation $a \in A$, for every element $i$ in the permutation $a$, all even elements in $a$ to the right of $i$ less than $i$ should be reversed (that is reordered to in increasing order); similarly to obtain a permutation in $A$ from a permutation $b \in B$, for every element $i$ in the permutation $b$, all even elements in $b$ to the right of $i$, less than $i$ should be reversed (that is reordered to in decreasing order). \todo{should have some justification here that reversing reordering these elements doesn't 'step on each other'... that is, you can always do it for some $i_1$ and then some $i_2$ afterward}
Since the mapping from $A$ to $B$ is clearly reversible, and hence invertible, we conclude that the mapping we just established between $A$ and $B$ is bijective.

@@

\begin{proof}
As before, proving the theorem is equivalent to proving that the $m^{th}$ term of $t_n(213)$ is equal to $2^{m-1}$, or that the number of permutations in $T_{2m}$ that avoid $213$ is equal to $2^{m-1}$.

@@

Note that even though we proved that the sequences $t_n(231)$ and $t_n(213)$ are both equivalent, the methods used to prove that each sequence is equal to the sequence $1, 2, 4, 8, \ldots$ are vastly different -- this is an interesting topic of research that we would like to pursue as future work.\todo{is this necessary? it seems frantic. Maybe if we're going to do this, we should also go back to the point about the $s_n$ proofs being different and say a little more}
